---
title: Literature Review on Critical Elements in Coal
author:
  - name: Kane Maxwell
    email: kane.maxwell@matrixgeoscience.com
    affiliation: Matrix Geoscience
    correspondingauthor: true
  - name: Yuhao Long
    email: ylon0012@student.monash.edu
    affiliation: Monash University
  - name: Evan Ginting
    email: egin0003@student.monash.edu
    affiliation: Monash University
address:
  - code: Matrix Geoscience
    organization: Matrix Geoscience
  - code: Monash University
    organization: Monash University Masters of Buisness Analytics

abstract: |
  This paper summarises the literature on critical elements contained in coal. Specifically the paper adresses the following questions: 
  
  1) What are critical elements, what are they used for and what is their projected demand?
  
  2) What types of critical elements are found in coal, and in what concentrations?
  
  3) What concentrations of critical elements would be considered economic to extract?
  
  4) Are there any existing coal mines, or coal basins that are extracting critical elements from coal, or coal tailings?
  
  5) What analytical and processing methods can be used to extract critical elements from coal?
  
  
keywords: 
  - Coal
  - Critical Elements
  - Rare Earth Elements
journal: "International Journal of Coal Geology"
date: "`r Sys.Date()`"
linenumbers: false
numbersections: true
bibliography: mybibfile.bib
biblio-style: elsarticle-harv # author year style for natbib - use 'elsarticle-num' or 'elsarticle-num-names' for numbered scheme
classoption: preprint, 3p, authoryear # remove authoryear is not using `elsarticle-harv`
# Use a CSL with `citation_package = "default"`
# csl: https://www.zotero.org/styles/elsevier-harvard
output: 
  rticles::elsevier_article:
    keep_tex: true
    citation_package: natbib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval =TRUE, warning = FALSE, message=FALSE)

library(gt)
library(tidyverse)
library(gtExtras)
```

# Critical elements overview

Answer the following question: 


1. What are critical elements (also referred to as critical minerals including rare earth elements)? What are they used for and what is their projected demand?

As the burgeoning ideology of environmental sustainability and geopolitical tension, The concept of critical elements received paramount attentions in the contemporary global landscape. Critical elements, or also referred as critical minerals, is vital  metallic or non-metallic element that underpin the functionality and advancement of core technologies, economic frameworks, and national security but may be susceptible for exogenous risk in supply chain. 

According to [Critical Minerals Strategy 2023–2030](https://www.industry.gov.au/publications/critical-minerals-strategy-2023-2030) issued by  @geoscience2023,There has total 15 elements are listed as top vulnerability for the future (Table 1, @Coyne2023 & @Skirrow2013 ):


           
```{r table1 }
table1<-tibble("Critical element"=c("Aluminum & derivative(Al)","Cobalt(Co)","Gallium(Ga)","Germanium(Ge)",
                            "Lithium(Li)","Magnesium(Mg)","Manganese(Mn)", "Nickel(Ni)","Rare-earth elements(REE)", "Silicon(Si)", "Tantalum(Ta)", "Titanium(Ti)","Tungsten(W)","Vanadium(V)","Zirconium(Zr)"),
               "Production(Kt)"=c(20,5.9,"-","-",61,2.6,3.3,150,18,0.05,0.057,0.85,"-","-",0.5),
               "% of Global production" =c("14%","3%","-","-","47%","10%","17%","4.5%","6%","1%","3%","8.4%","-","-","36%"),
    "Ore reserve(Kt)"=c("1,160",613,"-","-","4,563"," Not available","120,000",20.4,"3,121","-",49.8,"82,100",213,"2,948","29,200"),
  "Usage"=c("Aerospace sector and coating in Li-ion batteries","Li-ion battery cathodes,superalloys, steel, and magnets","ICs, GaN laser diodes and photovoltaics films","Fiber/infared optics,Polymerization Catalysts and semiconductors","Li-ion batteries and Lithium carbonate and lithium oxide in glass or ceramics","Pyrotechnics, medicine and nanocomposites in automotive/aerospace","Steel,Agricultral fertiliser and dry cell batteries", "Non-ferrous alloys,magnets and electroplating","Catalyst,magnets and polishing","Silicon wafer in electronic & photovoltaic cells and synthetic polymers", "Micro-capacitors and medical technology", "Aerospace and marine application or pigment through Titanium dioxide","Lightning and chemical compunds","Steel alloys","Cladding fuel rods in nuclear reactors")
    
    )
                                           
REE<- table1 |> filter(`Critical element`=="Rare-earth elements(REE)")|>
  pull(`Critical element`)

table1 |>gt()|> cols_align(
    align = "center" ) |>  
  gt_theme_538() |>
  tab_source_note(
    source_note = md(
      "Source: Skirrow et al., 2013 & Coyne and Campbell, 2023"
    )
  ) |>  tab_footnote(
    footnote = md("17 elements, including lanthanoid,Scandium(Sc) and Yttrium(Y)."),
    locations = cells_body(
      columns = `Critical element`,
      rows=`Critical element`== REE
    )
  ) |> 
    tab_footnote(
    footnote = md("data collected in 2012."),
    locations = cells_body(
      columns = names(table1)[4],
      rows=`Ore reserve(Kt)`==20.4
    )
  ) |>
  tab_header(title = "Table 1: summary of crtical element in Australia") |>
  cols_width(everything() ~ px(100))|>
  tab_options(
    table.font.size = px(10)# Adjust the font size
  )

```



Rare-earth elements,a significant branch in critical element, comprise of 15 element in lanthanoid family and 2 extra elements with similar chemical properties--Scandium(Sc) and Yttrium(Y). Unlike name implication, albeit their overall natural abundance(NA) in earth crust is not extremely rare (average 180-200 ppm) their distribution in earth is quite scattered and strong  propensity to coexist in pairs or group within ore deposits in terms of geochemical properties. Therefore, only few REE can be concentrated to a degree that permits for commercial mining. The largest segment of global consumption is catalyst(24%) in automotive or petrochemical industry, as well as  equally high demand(23%) in magnet(NdFeB, SmCo etc.) @Zhou2017.

With the exuberant demand shock from EVs and clean energy exploration, the consumption of critical minerals is foreseeable to be thrived: Geoscience Australia estimates that by 2040, critical elements related to lithium batteries (such as Li, Co, and Ni) will see an exponential surge of 20 to 40 times, while REEs (rare earth elements) will see a 7-fold increase during the same period.




# Critical elements in coal

Answer the following question: 

2. What types of critical elements are found in coal, and in what concentrations?
 In an ideal state, any chemical elements can be detected in coal deposit, which may originate from syn-genetic plant decays or epigenetic source after . Its concentration will be determined on coalified compaction and the heat & pressure environment.



In @Hodgkinson2020 element mapping  project on Bowen basin,the largest coal reserves in Australia, the concentration of element  composition is subjective to sample's lithology rather than the depth grading:


1). In coal and derivative,  albeit majority of element concentrations is inferior of the benchmark against earth crust average, local  samples exhibit  enrichment in HREE and Scandium in respect to @McLennan2011 Post-Archaean Australian Shales (PAAS) standard , while abnormal 4-6 times higher than crustal average in moderate  critical element, Bismuth(Bi) .

2). Siltstone and mudstone has a lackluster finding to classify enrichment for majority of elements concentration,except for  the concentration of Cobalt compound barely meet crustal average,  whose ubiquitous economic value may warrant further examination.

3).  As the sediment from volcanic ash, tuffaceous rock is rich in pumice and lithic fragments. The sample display a series of  elevated concentrations of  strategic elements including REE, Ga and Bi. Besides, a potential Lithium-rich borehole is found, with approximate 5 times higher than crustal average.

Below is the summary result (Table 2) from  the distribution of critical element :


```{r table2}
table2_c<-tibble("Critical element"=c("Lithium","REE","Cobalt","Nickel","Tantalum","Vanadium","Zirconium","Gallium","Bismuth"),
       "Crust"=c(21,184,17,47,1,97, 193,17,0.2),
       "Average concentration(ppm)"= c(13.7,115.8,16.9,11.2,0.33,85.6,102.1,12.3,0.59),
       "Higest concentration(ppm)"=c(25,205,30,40,1,140,160,25,1),
                                     
       "% of above crustal average"=c(2/9,1/9,4/9,0,1/3,2/9,0,4/9,2/3),
       "Type"=rep("Coal& associate",9)
       )



table2_sm<-tibble(
  "Critical element"=c("Lithium","REE","Cobalt","Nickel","Tantalum","Vanadium","Zirconium","Gallium","Bismuth"),
       "Crust"=c(21,184,17,47,1,97,193, 17,0.2),
  "Average concentration(ppm)"= c(17.2,138.8,39.3,25.8,0.2,102,116.8,15,0.18),
       "Higest concentration(ppm)"=c(28,189,134,73,1,225,243,22,0.4),
                                     
       "% of above crustal average"=c(1/3,1/6,2/3,1/3,1/6,1/3,1/6,1/3,2/3),
       "Type"=rep("Siltstone & mudstone",9)
)


table2_tf<-tibble(
  "Critical element"=c("Lithium","REE","Cobalt","Nickel","Tantalum","Vanadium","Zirconium","Gallium","Bismuth"),
       "Crust"=c(21,184,17,47,1,97,193, 17,0.2),
  "Average concentration(ppm)"= c(21.5,244,9.25,3.75,1.1,27.9,153.75,32.25,0.71),
       "Higest concentration(ppm)"=c(105,441,19,30,2,70,282,37,1.2),
                                     
       "% of above crustal average"=c(1/8,7/8,1/8,0,1,0,1/4,1,1),
       "Type"=rep("Tuffaceous rocks",9)
)

table2_bind<-rbind(table2_c,table2_sm,table2_tf)
table2_bind |> 
  group_by(Type) |>
  gt()|>  
  gt_theme_538() |>
  cols_align(align = "center" )|> 
  fmt_percent("% of above crustal average",
                                decimals=2) |> 
  tab_header(title = "Table 2: summary of Hodginkson et al., 2021  sampling mapping result  for Bowen basin's sample")|>
   tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = "Average concentration(ppm)",
      rows=`Average concentration(ppm)`>= Crust
    )
  )|>
  tab_source_note(
    source_note = md(
      "Source: Hodginkson et al., 2020"
    )
  )  |> tab_footnote(
    footnote = " McLennan 2011  Post-Archean
Australian Shale standard ",
    locations = cells_column_labels(columns = Crust)
  )|>
  tab_header(title = "Table 2: summary of crtical element in Australia") |>
  cols_width(everything() ~ px(100))|>
  tab_options(
    table.font.size = px(10)# Adjust the font size
  )

```


# Economic concentrations

Answer the following question: 

3. What concentrations of critical elements (including rare earth elements) would be considered economic to extract from coal?

The booming demand for critical element, has not merely driven interest in alternative sources beyond traditional mining but also stimulate the exploration of operational feasibility from an economic value perspective. Economic  assessment is hinged with the priority concern on concentrations, as well as demand-supply dynamic and operational cost @usde2017.

In general, @Seredin2012 study for the coal mining in Far east region, Russia manifest the cut-off  criterion for REE extraction will range from 800-1000 ppm, subject to seam thickness of the coal. However, the primitive cut-off grading does not correct reflect market trend on each individual composition. The new outlook coefficient(Table 3) is introduced to lever the economic degree of rarity for REY oxide(REO). Elements with plentiful deposits or relatively narrow application markets will be graded as 'Excessive', vice versa to be graded as 'Vital'. The ratio formula can be written as:

$$ \tag{1} C_{Outlook}=\frac{\sum{C_{Vital}}}{\sum{C_{Excessive}}}  $$
$$ \tag{2} C_{\text{Critical percent}}=\frac{\sum{C_{Vital}}}{\sum{C_{REE}}} $$

```{r table3}
table3<-tibble("REE"= c("Scandium(Sc)","Yttrium(Y)", "Lanthanum (La)", "Cerium (Ce)", "Praseodymium (Pr)", "Neodymium (Nd)", "Promethium (Pm)", "Samarium (Sm)", "Europium (Eu)", "Gadolinium (Gd)", "Terbium (Tb)", "Dysprosium (Dy)", "Holmium (Ho)", "Erbium (Er)", "Thulium (Tm)", "Ytterbium (Yb)", "Lutetium (Lu)"),
   "Category"= c("-", "M", "L","L","L","L","-","L","M","M","M","M","H","H","H","H","H"),
   "Significance"=c("-","Vital","Moderate","Excessive","Moderate","Vital",
                    "-", "Moderate","Vital","Moderate","Vital","Vital","Excessive","Vital","Excessive","Excessive","Excessive")
   )

table3 |>gt()|>
  cols_align(align = "center" ) |>  
  gt_theme_538() |> tab_footnote(
    footnote = "L- Light; M- Middle; H- Heavy",
    locations = cells_column_labels(columns = Category)
  )|> 
    tab_footnote(
    footnote = md("Not included due to heterogeneous and radioactive reason."),
    locations = cells_body(
      columns =Significance,
      rows=Significance =="-"
    )
  ) |>  tab_source_note(
    source_note = md(
      "Source: Seredin et al., 2012"
    )
  ) |>
  tab_header(title = "Table 3: summary of crtical element in Australia") |>
  cols_width(everything() ~ px(100))|>
  tab_options(
    table.font.size = px(10)# Adjust the font size
  )
```


@Ketris2009 research measured average trace REE concentration globally at 403.5 ppm, with an approximately 1 outlook coefficient and 35% $C_{\text{Critical percent}}$. Continual research by @Choudhary2022 analyzed approximately 288 coal,fly ash samples, reporting 11 of 13 nations has been detected above-average case, especially  notably enrichment in China, Russia and Central Asia.


Furthermore, @DaiFinkelman2018 also compiled the cut-off grade(Table 4) for key elements in coal.

```{r table4}
table4<-tibble("Element"= c("Uranium(U)","Germanium(Ge)*","Vanadium(V)*","Scandium(Sc)*","Selenium(Se)", "Niobium(Nb)", "Zirconium(Zr)*","Molybdenum(Mo)","Rhenium(Re)","Tungsten(W)*","Antimony(Sb)","Beryllium(Be)"),
"Cut-off grade"= c(1000,300,1000,100,"500-800", 300,2000,1000,1,1000,100,300)
   )

hd_ree<- table4|> 
  filter(Element %in% c("Germanium(Ge)*","Vanadium(V)*","Scandium(Sc)*","Zirconium(Zr)*",
                       "Tungsten(W)*" ))|> pull(Element)

table4 |>gt()|>
  cols_align(align = "center" ) |>  
  gt_theme_538() |>
    tab_footnote(
    footnote = md("High-demand critical element"),
    locations = cells_body(
      columns =Element,
      rows= Element ==hd_ree
    )
  )  |>  tab_source_note(
    source_note = md(
      "Source: Dai et al., 2018"
    )
  ) |>
  tab_header(title = "Table 4: summary of crtical element in Australia") |>
  cols_width(everything() ~ px(100))|>
  tab_options(
    table.font.size = px(10)# Adjust the font size
  )
```



# Existing economic deposits

Answer the following question: 

4. Are there any existing coal mines, or coal basins that are extracting critical elements from coal, or coal tailings?

The extraction of critical elements from coal mines is still in the observation and exploration stage. Industrial-grade  REE and lithium deposits have been respectively probed in the Jungar basin in Inner Mongolia and the Ningwu basin in Shanxi Province, China. @sun2010  study on the Antaibao surface coalfield(Ningwu basin) found  Lithium  enrichment with 10 times higher than China WAV  in roof rock, floor rock and coal seams. Another independent anlysis  @Dai2012 of mineralogical and geochemical compositions in 
Daqingshan coalfield(Jungar basin) exhibits L-type or H-type of REY ,Ga  and $Al_{2}O_3$ abnormalities in coal bench, widely distributed in chlorite,kaolinite and goyazite.

# Extraction of critical elements

Answer the following question: 

5. What analytical and processing methods can be used to extract critical elements from coal?

Try @Eterigho2021 for REE extraction example. Also look at @Qin2015 and Qin2015b 


# References {-}

