---
title: Literature Review on Critical Elements in Coal
author:
  - name: Kane Maxwell
    email: kane.maxwell@matrixgeoscience.com
    affiliation: Matrix Geoscience
    correspondingauthor: true
  - name: Yuhao Long
    email: ylon0012@student.monash.edu
    affiliation: Monash University
  - name: Evan Ginting
    email: egin0003@student.monash.edu
    affiliation: Monash University
address:
  - code: Matrix Geoscience
    organization: Matrix Geoscience
  - code: Monash University
    organization: Monash University Masters of Buisness Analytics

abstract: |
  This paper summarises the literature on critical elements contained in coal. Specifically the paper adresses the following questions: 
  
  1) What are critical elements, what are they used for and what is their projected demand?
  
  2) What types of critical elements are found in coal, and in what concentrations?
  
  3) What concentrations of critical elements would be considered economic to extract?
  
  4) Are there any existing coal mines, or coal basins that are extracting critical elements from coal, or coal tailings?
  
  5) What analytical and processing methods can be used to extract critical elements from coal?
  
  
keywords: 
  - Coal
  - Critical Elements
  - Rare Earth Elements
journal: "International Journal of Coal Geology"
date: "`r Sys.Date()`"
linenumbers: false
numbersections: true
bibliography: mybibfile.bib
biblio-style: elsarticle-harv # author year style for natbib - use 'elsarticle-num' or 'elsarticle-num-names' for numbered scheme
classoption: preprint, 3p, authoryear # remove authoryear is not using `elsarticle-harv`
# Use a CSL with `citation_package = "default"`
# csl: https://www.zotero.org/styles/elsevier-harvard
output: 
  rticles::elsevier_article:
    keep_tex: true
    citation_package: natbib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval =TRUE, warning = FALSE, message=FALSE)

library(gt)
library(tidyverse)
library(gtExtras)
```

# Critical elements overview

Answer the following question: 


1. What are critical elements (also referred to as critical minerals including rare earth elements)? What are they used for and what is their projected demand?

As the burgeoning ideology of environmental sustainability and geopolitical tension, The concept of critical elements received paramount attentions in the contemporary global landscape. Critical elements, or also referred as critical minerals, is vital  metallic or non-metallic element that underpin the functionality and advancement of core technologies, economic frameworks, and national security but may be susceptible for exogenous risk in supply chain. 

According to [Critical Minerals Strategy 2023–2030](https://www.industry.gov.au/publications/critical-minerals-strategy-2023-2030) issued by  @geoscience2023,There has total 15 elements are listed as top vulnerability for the future (Table 1, @Coyne2023 & @Skirrow2013 ):


           
```{r table1 }
table1<-tibble("Critical element"=c("Aluminum & derivative(Al)","Cobalt(Co)","Gallium(Ga)","Germanium(Ge)",
                            "Lithium(Li)","Magnesium(Mg)","Manganese(Mn)", "Nickel(Ni)","Rare-earth elements(REE)", "Silicon(Si)", "Tantalum(Ta)", "Titanium(Ti)","Tungsten(W)","Vanadium(V)","Zirconium(Zr)"),
               "Production(Kt)"=c(20,5.9,"-","-",61,2.6,3.3,150,18,0.05,0.057,0.85,"-","-",0.5),
               "% of Global production" =c("14%","3%","-","-","47%","10%","17%","4.5%","6%","1%","3%","8.4%","-","-","36%"),
    "Ore reserve(Kt)"=c("1,160",613,"-","-","4,563"," Not available","120,000",20.4,"3,121","-",49.8,"82,100",213,"2,948","29,200"),
  "Usage"=c("Aerospace sector and coating in Li-ion batteries","Li-ion battery cathodes,superalloys, steel, and magnets","ICs, GaN laser diodes and photovoltaics films","Fiber/infared optics,Polymerization Catalysts and semiconductors","Li-ion batteries and Lithium carbonate and lithium oxide in glass or ceramics","Pyrotechnics, medicine and nanocomposites in automotive/aerospace","Steel,Agricultral fertiliser and dry cell batteries", "Non-ferrous alloys,magnets and electroplating","Catalyst,magnets and polishing","Silicon wafer in electronic & photovoltaic cells and synthetic polymers", "Micro-capacitors and medical technology", "Aerospace and marine application or pigment through Titanium dioxide","Lightning and chemical compunds","Steel alloys","Cladding fuel rods in nuclear reactors")
    
    )
                                           
REE<- table1 |> filter(`Critical element`=="Rare-earth elements(REE)")|>
  pull(`Critical element`)

table1 |>gt()|> cols_align(
    align = "center" ) |>  
  gt_theme_538() |>
  tab_source_note(
    source_note = md(
      "Source: Skirrow et al., 2013 & Coyne and Campbell, 2023"
    )
  ) |>  tab_footnote(
    footnote = md("17 elements, including lanthanoid,Scandium(Sc) and Yttrium(Y)."),
    locations = cells_body(
      columns = `Critical element`,
      rows=`Critical element`== REE
    )
  ) |> 
    tab_footnote(
    footnote = md("data collected in 2012."),
    locations = cells_body(
      columns = names(table1)[4],
      rows=`Ore reserve(Kt)`==20.4
    )
  ) |>
  tab_header(title = "Table 1: summary of crtical element in Australia") |>
  cols_width(everything() ~ px(100))|>
  tab_options(
    table.font.size = px(10)# Adjust the font size
  )

```



Rare-earth elements,a significant branch in critical element, comprise of 15 element in lanthanoid family and 2 extra elements with similar chemical properties--Scandium(Sc) and Yttrium(Y). Unlike name implication, albeit their overall natural abundance(NA) in earth crust is not extremely rare (average 180-200 ppm) their distribution in earth is quite scattered and strong  propensity to coexist in pairs or group within ore deposits in terms of geochemical properties. Therefore, only few REE can be concentrated to a degree that permits for commercial mining. The largest segment of global consumption is catalyst(24%) in automotive or petrochemical industry, as well as  equally high demand(23%) in magnet(NdFeB, SmCo etc.) @Zhou2017.

With the exuberant demand shock from EVs and clean energy exploration, the consumption of critical minerals is foreseeable to be thrived: Geoscience Australia estimates that by 2040, critical elements related to lithium batteries (such as Li, Co, and Ni) will see an exponential surge of 20 to 40 times, while REEs (rare earth elements) will see a 7-fold increase during the same period.




# Critical elements in coal

Answer the following question: 

2. What types of critical elements are found in coal, and in what concentrations?

For good background info relevant to Australia please start with the ACARP report (C29030) by @Hodgkinson2021. Also, in our data analysis we will be focusing on determining PAAS values - make sure you know what this means and how to calculate this - it is fully explained in  @Hodgkinson2021.


# Economic concentrations

Answer the following question: 

3. What concentrations of critical elements (including rare earth elements) would be considered economic to extract from coal?

You might try the Report on Rare Earth Elements from Coal and Coal Byproducts (@usde2017) to start with.

Also try @Seredin2012; @Dai2016; @Qin2015b; @SUN2014.



# Existing economic deposits

Answer the following question: 

4. Are there any existing coal mines, or coal basins that are extracting critical elements from coal, or coal tailings?

Try @Qin2015b to start with. Also try @Sun2010 and @Qin2015

# Extraction of critical elements

Answer the following question: 

5. What analytical and processing methods can be used to extract critical elements from coal?

Try @Eterigho2021 for REE extraction example. Also look at @Qin2015 and Qin2015b 


# References {-}

